\huge A Better (One-Line!) Title Here

### 2016-10-17 pets2017-paper/pets2017-paper.tex
made running title match temp title
finshed pass through background section.

  \runningtitle{Ugh!}

@@

However, we believe that our work uniquely necesssary and beneficial to Tor Browser. Although originally designed for Internet anonymity, using Tor Browser to circumvent censorship has now become sufficiently common that many countries now attempt to block Tor relays for this reason~\cite{winter2012great}. Our experiment to design an easier bootstrapping process will especially benefit citizens who face Internet censorship. If successful, an increase in overall users means more than user growth, but an increased anonymity set~\cite{dingledine2006anonymity}. \\

@@

Bridges are unlisted Tor relays that can serve as the entry node to the Tor network.
Bridges can be simple, unlisted relays. 
But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand), protocols that obfuscates Tor's network protocol. 
Most transports obfuscate traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Some transports route traffic through other services to obfuscate the traffic, avoiding the need for a secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.
Bridges and transports make it possible to connect to the Tor network even if a censor has blocked all publicly listed relays and are blocking any packets that look like the Tor network protocols. Fig.~\ref{fig:bridge-options} paraphrases the bridge and pluggable transport options at the time of the study.

@@

In addition to Tor-specific components, a local proxy may be necessary to connect 
outside the local network in managed environments, such as corporate or university networks.
(Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. Fig.~\ref{fig:topology} illustrates the interacting components.

@@

\subsection{Light, Heavy, and Corporate Censorship}

\subsection{Connections to Tor}

There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy 
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. In the worst case, users must know or find out:\\

\begin{itemize}
	\item{Whether their Internet connection is censored} 
	\item{Whether the Tor network is censored by their ISP}
	\item{Which hard-coded bridges work in their country} 
	\item{If no hard-coded bridges work, how to get custom bridge information and connect to it} 
	\item{Whether a proxy is required to access the Internet}
	\item{If a proxy is required, and if so, the proxy settings}
\end{itemize}

Uncensored users and users in censorship environments that do not explicitly 
block Tor do not require a bridge or a proxy and can bypass these steps in the configuration process.
Users in censorship environments that explicitly block Tor but have not blocked the 
hard-coded bridges in the Tor Launcher source code are required to use a 
hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
blocked Tor relays and hard-coded bridges are required to configure a meek bridge (which 
routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
configure a custom bridge to connect to Tor.

%Configuring a bridge requires providing one or more
%``bridge lines,'' a specification of a bridge that
%includes its IP address, transport type, and other metadata.
%For ease of use, the interface has hard-coded options for 
%the user to choose a group of bridges that use a particular
%pluggable transport. For example, choosing  the hard-coded obfs3 option
%configures a handful of bridges that use obfs3 pluggable transport.
%Some censors block the IP addresses of the hard-coded bridges by looking
%at the source code for those addresses (except flashproxy and meek).
%If the built-in bridges do not work, a user can obtain bridge lines
%through out-of-band channels, for instance by email~\cite{bridgedb}.

%Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields. There is no assistance or automation with this process. The user must locate the  proxy information and correctly input this information.

@@

@@

\begin{description}
\item [E1: Mild censorship.]
(Representative of countries such as France and Australia.)
The E1 environment only blocks some websites,
as if by DNS poisoning.
We blocked subdomains of torproject.org
and wikipedia.org.
(The participants' main goal in the experiment was to read a page on en.wikipedia.org.)
To succeed in this environment,
participants only had to click ``Connect'' on the first screen;
additional configuration was optional.

\item [E2: Intermediate censorship.]
(Representative of countries such as Tunisia.)
The E2 environment blocks websites as in E1 and
additionally blocks IP addresses of public Tor relays
and directory authorities, simulating a censor who knows
about circumvention and tries to stop it.
In this environment, simply clicking ``Connect'' does not work;
participants had to select a built-in bridge
(any type other than ``flashproxy'' would work).
A custom bridge would work but was not necessary.

\item [E3: Comprehensive censorship.]
(Representative of countries such as China and Syria.)
The E3 environment blocks websites and Tor relays like E1 and E2
and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
To succeed in this environment, participants had to select
one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
or acquire their own custom bridge and enter it manually.
\end{description}

@@

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of a built-in bridge;
and E3 requires selection of a specific type of built-in bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

>>>>

  \runningtitle{A Better (One-Line!) Title Here}

@@

However, we believe that our work uniquely necesssary and beneficial to Tor Browser. Although originally designed for Internet anonymity, using Tor Browser to circumvent censorship has now become sufficiently common that many countries now attempt to block Tor relays for this reason~\cite{winter2012great}. Our contributions toward an easier bootstrapping process will especially benefit citizens who face Internet censorship. If there is an increase in overall users as a result, they add a security bonus by increasing the anonymity set~\cite{dingledine2006anonymity}. \\

@@

Bridges are unlisted Tor relays that can serve as an alternative entry node.
Bridges can be simple, unlisted relays. 
But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates the traffic. 
Most transports disguise traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Some transports route traffic through other services, avoiding the need for a secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.
Bridges and transports allow a connection to the Tor network when all publicly listed relays and any Tor-looking packets are blocked. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.

@@

In addition to Tor-specific components, a local proxy is required to connect 
in certain managed networks.
(Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. Fig.~\ref{fig:topology} illustrates the interacting components.

@@

\subsection{State and Corporate Censorship}
State level censors can vary in their thoroughness in censorship, resulting in a variety of ever-changing network conditions. Some DNS-poison websites they want to block, while others that employ more sophisticated techniques, such as deep packet inspection and protocol detection. In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship. In other countries, sophisticated state-level censorship require bridges that run specific tranports that route traffic through other, non-Tor services first. For example, only meek-amazon and meek-azure transports work to bypass China's GFW.

Some companies and educational institutions have a firewall, which can be bypassed by a proxy (with or without Tor). The users behind a corporate firewall represent a very small fraction of censored users.

\subsection{Connecting to Tor}

%\begin{itemize}
%	\item{Whether their Internet connection is censored} 
%	\item{Whether the Tor network is censored by their ISP}
%	\item{Which hard-coded bridges work in their country} 
%	\item{If no hard-coded bridges work, how to get a custom bridge and connect to it} 
%	\item{Whether a proxy is required to access the Internet}
%	\item{If a proxy is required, and if so, the proxy settings}
%\end{itemize}

Configuring a bridge requires providing one or more
``bridge lines,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields. The user must locate and input this information.

There are many valid configuration settings to connect to the Tor network.
For instance, a user who needs a bridge but not need a proxy can connect to Tor with a bridge and proxy, provided that both were configured correctly. The set of valid configuration settings vary on the censorship environment.

@@

Because proxies are not Tor-specific concept and affects a small fraction of the Internet population, we study connections to Tor that require a bridge but not a proxy. We focus our attention on the parts of the configuration interface that set up bridges and simulate environments that do not need a proxy. However, connections to Tor are still considered valid in the experiment.

@@

\begin{description}
\item [E1: Mild censorship.]
The E1 environment only blocks some websites,
as if by DNS poisoning.
We blocked subdomains of torproject.org
and wikipedia.org.
(The participants' main goal in the experiment was to read a page on en.wikipedia.org.)
To succeed in this environment,
participants only had to click ``Connect'' on the first screen;
additional configuration was optional.

\item [E2: Intermediate censorship.]
The E2 environment blocks websites as in E1 and
additionally blocks IP addresses of public Tor relays
and directory authorities, simulating a censor who knows
about circumvention and tries to stop it.
In this environment, simply clicking ``Connect'' does not work;
participants had to select a built-in bridge
(any type other than ``flashproxy'' would work).
A custom bridge would work but was not necessary.

\item [E3: Comprehensive censorship.]
The E3 environment blocks websites and Tor relays like E1 and E2
and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
To succeed in this environment, participants had to select
one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
or acquire their own custom bridge and enter it manually.
\end{description}

@@

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires a built-in bridge;
and E3 requires a specific type of built-in bridge
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}
